Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-13 paper/Paper.tex
update contract interfaces

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward tokens ever generated as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.

@@

\subsection{TokenSale}
\begin{verbatim}
contract TokenSaleInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFunded;   
    address public privateSale;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

@@

The boolean \verb|isFunded| is true if DAO has reached its minimum funding goal, false otherwise.

@@

\subsection{DAO} \label{DAO}
\begin{verbatim}
contract DAOInterface {
    Proposal[] public proposals;
    uint minQuorumDivisor;
    uint lastTimeMinQuorumMet;
    address public serviceProvider;
    address[] public allowedRecipients;
    mapping (address => uint) public rewardToken;
    uint public totalRewardToken;
    ManagedAccount public rewardAccount;
    ManagedAccount public DAOrewardAccount;
    mapping (address => uint) public paidOut;
    mapping (address => uint) public DAOpaidOut;
    mapping (address => uint) public blocked;
    uint public proposalDeposit;
    DAO_Creator public daoCreator;

    struct Proposal {
        address recipient;
        uint amount;
        string description;
        uint votingDeadline;
        bool open;
        bool proposalPassed;
        bytes32 proposalHash;
        uint proposalDeposit;
        bool newServiceProvider;
        SplitData[] splitData;
        uint yea;
        uint nay;
        mapping (address => bool) votedYes;
        mapping (address => bool) votedNo;
        address creator;
    }

@@

    function DAO(
        address _defaultServiceProvider,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool _newServiceProvider
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function addAllowedAddress(address _recipient) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function isBlocked(address _account) returns (bool);

@@

The address \verb|serviceProvider| is set at the creation of the DAO and defines the service provider.

The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|serviceProvider|, \verb|rewardAccount|, \verb|extraBalance| and addresses in the whitelist. Only the \verb|serviceProvider| can add addresses to the whitelist.

@@

Similar, \verb|DAOrewardAccount| is also of the type \verb|ManagedAccount|. This account is used to receive all rewards from projects funded by the DAO. It will then redistribute them amongst all splitted DAOs as well as itself using \verb|retrieveDAOReward|.

@@

The map \verb|blocked| stores the addresses of the DAO Tokens that have voted and therefore are not allowed to be transferred until the vote has concluded.. The address points to the proposal ID.

@@

@@

A single proposal has the parameters:
\begin{description}
 \item[recipient] The address where the \verb|amount| of wei will go to if the proposal is accepted.
 \item[amount] The amount of wei to transfer to \verb|recipient| if the proposal is accepted.
 \item[description] A plain text description of the proposal.
 \item[votingDeadline] A unix timestamp, denoting the end of the voting period.
 \item[open] A boolean which is false if the votes have already been counted, true otherwise.
 \item[proposalPassed] A boolean which is true if a quorum has been achieved with the majority approving the proposal.
 \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
 \item[proposalDeposit] The minimum deposit (in wei) the creator of a proposal is required to send to submit a proposal. It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam. It is set to $20$ ether by default but the creator of the proposal can send any amount above this for the deposit.For Slock.it’s purposes, the proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal. The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO. 
 \item[newServiceProvider] A boolean which is true if this proposal assigns a new service provider.
 \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new service provider.
 \item[yea] Number of tokens in favor of the proposal.
 \item[nay] Number of tokens in opposed to the proposal.
 \item[votedYes] Simple mapping to check if a token holder has voted for it.
 \item[votedNo] Simple mapping to check if a token holder has voted against it.
 \item[creator] The address of the token holder that created the proposal.
\end{description}

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO''. This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|serviceProvider|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount| 
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
\end{itemize}

@@

\subsubsection*{newProposal}
This function is used to create a new proposal. The arguments of the function are:
\begin{description}
 \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current service provider or an address on the whitelist \verb|allowedRecipients|).
 \item[amount] The amount of wei to be sent in the proposed transaction.
 \item[description] A string describing the proposal.
 \item[transactionData] The data of the proposed transaction.
 \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 10 days for a new service provider proposal.
 \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
\end{description}
After checking the sanity of the proposal (see code), this function creates a proposal which is open for voting for a certain amount of time. The function will return a proposal ID which is used to vote.

@@

\subsubsection*{vote}
This function is used to vote on a proposal. The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[supportsProposal]  A boolean Yes/No does the DAO token holder support the proposal
\end{description}
The function simply checks whether the sender has yet to vote and whether the proposal is still open for voting. If both requirements are met, it records the vote in the storage of the contract. The tokens used to vote will be blocked, meaning they can not be transferred until the proposal is closed.This is to avoid voting several times with different sender addresses.

@@

\subsubsection*{splitDAO}
After a new service provider has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new service provider. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newServiceProvider] The address of the new service provider of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|getMyReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion of the reward tokens $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.

@@

\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

@@

@@

Reward tokens are generated when the DAO makes any transaction spending ether. When the DAO’s products send ether back to the DAO (for example when a Slock sends $1\%$ of a transaction to the DAO), the ether is held within \verb|DAOrewardAccount|. The DAO can use these rewards to fund new proposals or to equally distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).

Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount|b(a \verb|ManagedAccount| contract]. Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the 
If accepted, the complete DAO moves to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens. This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.

@@

    // Address of the service provider
    address public serviceProvider;
    // The whitelist: List of addresses the DAO is allowed to send money to
    mapping (address => bool) public allowedRecipients;

@@

        serviceProvider = _defaultServiceProvider;
        daoCreator = _daoCreator;
        proposalDeposit = _proposalDeposit;
        rewardAccount = new ManagedAccount(address(this));
        DAOrewardAccount = new ManagedAccount(address(this));
        if (address(rewardAccount) == 0)
            throw;
        if (address(DAOrewardAccount) == 0)
            throw;
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length++; // avoids a proposal with ID 0 because it is used

        allowedRecipients[address(this)] = true;
        allowedRecipients[serviceProvider] = true;
    }

@@

        // Sanity check
        if (_newServiceProvider && (
            _amount != 0
            || _transactionData.length != 0
            || _recipient == serviceProvider
            || msg.value > 0
            || _debatingPeriod < 1 weeks)) {
            throw;
        } else if(
            !_newServiceProvider
            && (!isRecipientAllowed(_recipient) || (_debatingPeriod < 2 weeks))
        ) {
            throw;
        }

@@

    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
        if (msg.sender != serviceProvider)
            throw;
        allowedRecipients[_recipient] = true;
        return true;
    }

@@

    address serviceProvider;
    bytes32 hashOfTheContract;
    uint minDailyCosts;
    uint paidOut;

@@

    modifier callingRestriction {
        if (promiseValid) {
            if (msg.sender != address(client))
                throw;
        } else if (msg.sender != serviceProvider) {
                throw;
        }
        _
    }

@@

    function SampleOffer(
        address _serviceProvider,
        bytes32 _hashOfTheContract,
        uint _totalCosts,
        uint _oneTimeCosts,
        uint _minDailyCosts,
        uint _rewardDivisor,
        uint _deploymentReward
    ) {
        serviceProvider = _serviceProvider;
        hashOfTheContract = _hashOfTheContract;
        totalCosts = _totalCosts;
        oneTimeCosts = _oneTimeCosts;
        minDailyCosts = _minDailyCosts;
        dailyCosts = _minDailyCosts;
        rewardDivisor = _rewardDivisor;
        deploymentReward = _deploymentReward;
    }

    function sign() {
        if (msg.value < totalCosts && dateOfSignature != 0)
            throw;
        if (!serviceProvider.send(oneTimeCosts))
            throw;
        client = DAO(msg.sender);
        dateOfSignature = now;
        promiseValid = true;
    }

@@

    function getDailyPayment() {
        if (msg.sender != serviceProvider)
            throw;
        uint amount = (now - dateOfSignature) / (1 days) * dailyCosts - paidOut;
        if (serviceProvider.send(amount))
            paidOut += amount;
    }

@@

    // interface for Slocks
    function payOneTimeReward() returns(bool) {
        if (msg.value < deploymentReward)
            throw;
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }

    // pay reward
    function payReward() returns(bool) {
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (serviceProvider.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }
}
\end{verbatim}

>>>>

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{DAO}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{DAO}}$ is the amount of reward tokens owned by this DAO, as explained in section \ref{RewardToken} (also see \verb|rewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{DAO}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.

@@

\subsection{TokenSale}
\begin{verbatim}
contract TokenSaleInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFueled;
    address public privateSale;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

@@

The boolean \verb|isFueled| is true if DAO has reached its minimum fueling goal, false otherwise.

@@

\subsection{DAO} \label{DAO}
\begin{verbatim}
contract DAOInterface {
    Proposal[] public proposals;
    uint minQuorumDivisor;
    uint lastTimeMinQuorumMet;
    address public curator;
    address[] public allowedRecipients;
    mapping (address => uint) public rewardToken;
    uint public totalRewardToken;
    ManagedAccount public rewardAccount;
    ManagedAccount public DAOrewardAccount;
    mapping (address => uint) public paidOut;
    mapping (address => uint) public DAOpaidOut;
    mapping (address => uint) public blocked;
    uint public proposalDeposit;
    uint sumOfProposalDeposits;
    DAO_Creator public daoCreator;

    struct Proposal {
        address recipient;
        uint amount;
        string description;
        uint votingDeadline;
        bool open;
        bool proposalPassed;
        bytes32 proposalHash;
        uint proposalDeposit;
        bool newCurator;
        SplitData[] splitData;
        uint yea;
        uint nay;
        mapping (address => bool) votedYes;
        mapping (address => bool) votedNo;
        address creator;
    }

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

@@

The address \verb|curator| is set at the creation of the DAO and defines the curator.

The list \verb|allowedRecipients| is commonly referred to as ‘’the whitelist.’’ The DAO can only send transactions to itself, the \verb|curator|, \verb|extraBalance| and addresses in the whitelist. Only the \verb|curator| can add addresses to the whitelist.

@@

Similar, \verb|DAOrewardAccount| is also of the type \verb|ManagedAccount|. This account is used to receive all rewards from projects funded by the DAO. It will then redistribute them amongst all splitted DAOs as well as itself using the function \verb|retrieveDAOReward|.

@@

The map \verb|blocked| stores the addresses of the DAO Tokens that have voted and therefore are not allowed to be transferred until the vote has concluded. The address points to the proposal ID.

@@

The integer \verb|sumOfProposalDeposits| is the sum of all proposal deposits of open proposals.

@@

A single proposal has the parameters:
\begin{description}
 \item[recipient] The address where the \verb|amount| of wei will go to if the proposal is accepted.
 \item[amount] The amount of wei to transfer to \verb|recipient| if the proposal is accepted.
 \item[description] A plain text description of the proposal.
 \item[votingDeadline] A unix timestamp, denoting the end of the voting period.
 \item[open] A boolean which is false if the votes have already been counted, true otherwise.
 \item[proposalPassed] A boolean which is true if a quorum has been achieved with the majority approving the proposal.
 \item[proposalHash] A hash to check validity of a proposal. Equal to \verb|sha3(_recipient, _amount, _transactionData)|.
 \item[proposalDeposit] The deposit (in wei) the creator of a proposal has send to submit a proposal. It is taken from the \verb|msg.value| of a \verb|newProposal| call; its purpose is to prevent spam. Its minimal value is set when the contract is deploayed as constructor parameter. But the creator of the proposal can send any amount above this for the deposit. The proposals will be sorted by the proposal deposit in the GUI, so in the case that a proposal is considered important, the creator of the proposal can deposit extra ether to “advertise” their proposal. The creator of the proposal will be refunded the entire deposit if quorum is reached, if it is not reached the deposit remains with the DAO. 
 \item[newServiceProvider] A boolean which is true if this proposal assigns a new service provider.
 \item[splitData] The data used to split the DAO. This data is gathered from proposals when they require a new service provider.
 \item[yea] Number of tokens in favor of the proposal.
 \item[nay] Number of tokens in opposed to the proposal.
 \item[votedYes] Simple mapping to check if a token holder has voted for it.
 \item[votedNo] Simple mapping to check if a token holder has voted against it.
 \item[creator] The address of the token holder that created the proposal.
\end{description}

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO''. This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

@@

\subsubsection*{newProposal}
This function is used to create a new proposal. The arguments of the function are:
\begin{description}
 \item[recipient] The address of the recipient of the ether in the proposal (has to be the DAO address itself, the current service provider or an address on the whitelist \verb|allowedRecipients|).
 \item[amount] The amount of wei to be sent in the proposed transaction.
 \item[description] A string describing the proposal.
 \item[transactionData] The data of the proposed transaction.
 \item[debatingPeriod] The amount of time to debate the proposal, at least 2 weeks for a normal proposal and at least 1 week for a new service provider proposal.
 \item[newServiceProvider] A boolean defining whether this proposal is for a new service provider or not.
\end{description}
After checking the sanity of the proposal (see code), this function creates a proposal which is open for voting for a certain amount of time. The function will return a proposal ID which is used to vote.

@@

\subsubsection*{vote}
This function is used to vote on a proposal. The arguments of the function are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[supportsProposal]  A boolean Yes/No does the DAO token holder support the proposal
\end{description}
The function simply checks whether the sender has yet to vote and whether the proposal is still open for voting. If both requirements are met, it records the vote in the storage of the contract. The tokens used to vote will be blocked, meaning they can not be transferred until the proposal is closed. This is to avoid voting several times with different sender addresses.

@@

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new service provider has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new service provider. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newServiceProvider] The address of the new service provider of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, ther may be remainders which stay with the DAO.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = T_{\text{sender}} \cdot \Xi_{\text{rewardAccount}} / T_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount| and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.

@@

\subsubsection*{changeAllowedRecipients}
This function can add/remove an address to/from the whitelist, \verb|allowedRecipients|. It can only be executed by the curator.

@@

\subsubsection*{getNewDAOAdress}
This is just a helper function to read the address of a newly created `split DAO`. It gets the proposal ID which was used for the split as input parameter and return the address of the new DAO.

@@

Reward tokens are generated when the DAO makes any transaction spending ether. When the DAO’s products send ether back to the DAO, the ether is held within \verb|DAOrewardAccount|. The DAO can use these rewards to fund new proposals or to fairly distribute the rewards to the reward token holders (using a proposal which gets voted on by the DAO token holders).

Then the token holders of the DAOs will be able to claim the ether they have earned for their contribution to the original DAO that issued the reward token. To do this the DAO retrieve its rewards by callling the \verb|retrieveDAOReward| function, with the paramter \verb|_toMembers| set to true, which send the rewards to the \verb|rewardAccount| (a \verb|ManagedAccount| contract).
Then and only then will the token holders of the DAOs be able to call the \verb|getMyReward| function and receive their ether.

@@

\section{Updates}
Although the code of the contract specified at a certain address in the Ethereum blockchain can not be changed, there might still be a need for a single member or the DAO as a whole to change the contracts.
Every single member can always split the DAO as described above and move their funds to a new DAO. From there they can move their funds to another new DAO with a new smart contract.
But in order to use a new code for the complete DAO one can simply create a new DAO contract with all the needed features and deploy it on the blockchain, and make a proposal to call the \verb|newContract| function with the address of the new contract as parameter.
If accepted, the complete DAO moves to the new contract, meaining, all ether and reward tokens are transferred to the new contract. In order to use the same underlying DAO tokens there, one can use the \verb|approve| function and give the new DAO the right to move the tokens. In the new contract this right should only be usable in restricted functions which are only callable by the owner of the tokens.
Another option is to create new tokens in the new contract based on the token distribution in the old contract. This can also be achieved by a proof that the old tokens are destroyed (sending to the $0$ address).
This process allows for the DAO to maintain static immutable code on the Ethereum blockchain, while still being able to be updated if the need arises.

@@

    // Address of the service provider
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send money to
    mapping (address => bool) public allowedRecipients;

@@

        curator = _defaultServiceProvider;
        daoCreator = _daoCreator;
        proposalDeposit = _proposalDeposit;
        rewardAccount = new ManagedAccount(address(this));
        DAOrewardAccount = new ManagedAccount(address(this));
        if (address(rewardAccount) == 0)
            throw;
        if (address(DAOrewardAccount) == 0)
            throw;
        lastTimeMinQuorumMet = now;
        minQuorumDivisor = 5; // sets the minimal quorum to 20%
        proposals.length++; // avoids a proposal with ID 0 because it is used

        allowedRecipients[address(this)] = true;
        allowedRecipients[curator] = true;
    }

@@

        // Sanity check
        if (_newServiceProvider && (
            _amount != 0
            || _transactionData.length != 0
            || _recipient == curator
            || msg.value > 0
            || _debatingPeriod < 1 weeks)) {
            throw;
        } else if(
            !_newServiceProvider
            && (!isRecipientAllowed(_recipient) || (_debatingPeriod < 2 weeks))
        ) {
            throw;
        }

@@

    function addAllowedAddress(address _recipient) noEther external returns (bool _success) {
        if (msg.sender != curator)
            throw;
        allowedRecipients[_recipient] = true;
        return true;
    }

@@

    address curator;
    bytes32 hashOfTheContract;
    uint minDailyCosts;
    uint paidOut;

@@

    modifier callingRestriction {
        if (promiseValid) {
            if (msg.sender != address(client))
                throw;
        } else if (msg.sender != curator) {
                throw;
        }
        _
    }

@@

    function SampleOffer(
        address _curator,
        bytes32 _hashOfTheContract,
        uint _totalCosts,
        uint _oneTimeCosts,
        uint _minDailyCosts,
        uint _rewardDivisor,
        uint _deploymentReward
    ) {
        curator = _curator;
        hashOfTheContract = _hashOfTheContract;
        totalCosts = _totalCosts;
        oneTimeCosts = _oneTimeCosts;
        minDailyCosts = _minDailyCosts;
        dailyCosts = _minDailyCosts;
        rewardDivisor = _rewardDivisor;
        deploymentReward = _deploymentReward;
    }

    function sign() {
        if (msg.value < totalCosts && dateOfSignature != 0)
            throw;
        if (!curator.send(oneTimeCosts))
            throw;
        client = DAO(msg.sender);
        dateOfSignature = now;
        promiseValid = true;
    }

@@

    function getDailyPayment() {
        if (msg.sender != curator)
            throw;
        uint amount = (now - dateOfSignature) / (1 days) * dailyCosts - paidOut;
        if (curator.send(amount))
            paidOut += amount;
    }

@@

    // interface for Slocks
    function payOneTimeReward() returns(bool) {
        if (msg.value < deploymentReward)
            throw;
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (curator.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }

    // pay reward
    function payReward() returns(bool) {
        if (promiseValid) {
            if (client.DAOrewardAccount().call.value(msg.value)()) {
                return true;
            } else {
                throw;
            }
        } else {
            if (curator.send(msg.value)) {
                return true;
            } else {
                throw;
            }
        }
    }
}
\end{verbatim}
